\documentclass[a4paper,11pt]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{listings}

\title{Report 1}

\begin{document}

\section{Weekly Meeting(s):}
Meeting time: 6:00 pm - 9:30 pm (3 1/2 hours)\\
All team members present

\section{Deliverables achieved:}
\begin{enumerate}
\item	onboarding: setup repos, Git, IDE (intelliJ/VIM)
\item determined our Github workflow
\item reviewed the rules of the game and played a mock round
\item decided that we are going to use Java and JavaFX
\item set up our re-occuring out-of-class meeting (Thursdays 6:00pm-8:00pm)
\end{enumerate}

\section{Action Items due Tuesday January 23rd:}
\begin{enumerate}
\item type and share Github workflow (Carolyne)
\item look into purchasing game (Carolyne)
\item post questions on CU Learn (Akhil)
\item finalize progress report (together) - see progress report information below from prof
\item Read rules (Carolyne)
\item Weekly Report Template (Carolyne)
\item Set up Trello (Carolyne)
\item Meeting Sunday at noon - max 1

\end{enumerate}

\section{Scenario:}
\paragraph{}
Your first progress report is due Tuesday the 23rd (see its details under Topic 1)
In this first one, we want to specifically see a set of scenarios that you develop to test the game.
We are NOT imposing any particular syntax to use for you to describe this scenarios.
We want as few scenarios as possible that test as many of the features you plan to implement in this first iteration.
Think of a scenario as the description of a game:
\paragraph{}

\begin{lstlisting}
For example:
scenario 1:
game is set up for 3 players
player 1 receives <some list of cards>
player 2 receives <some list of cards>
player 3 receives <some list of cards>
quest "Boar Hunt" is drawn by player 1 who accepts setting it up
stage 1: <some list of cards> stage 2: <some list of cards>
player 2 is asked if she participates and declines
player 3 is asked if he participates and accepts
player 3 gets one adventure card and stage 1 is resolved: player 3 does 
	not pass stage 1
player 1 discards cards used for the quest and replaces them
-etc.	
\end{lstlisting}

\paragraph{}
That is, before coding, decide on the features you are going for and write a corresponding test plan (which will evolve).
\paragraph{}
A feature is a SMALL piece of functionality: it must be codable and tested in hours or very few days, not weeks.
\paragraph{}
That means, you MUST break big requirements into small features...
\paragraph{}
Rank your features in decreasing order of importance (as it is likely you will not get to the latter ones...)
\paragraph{}
Then decide on the language and tools and set up your repository. (DONE)
\paragraph{}
Then do NOT distribute all features among team members.
\paragraph{}
Instead, starting with the most important ones, tackle them so that you DO complete at least one by the time your progress report is due.
\paragraph{}
Remember: the ability to 'rig' your game (by assigning specific cards to specific players and setting up the decks) is crucial for the testability of your project. This is an implicit requirement since it is not something a customer will ask for BUT it is something you must provide in order to demonstrate to the customer that you have satisfied his requirements.


\end{document}
